Blockchain in the Industrial Sector

### 2020-04-29 paper.tex
Remove sectiosn from related works

\section{Related Work}
The topic of this thesis involves two domains, the manufacturing industry, and the blockchain technology. To identify the relevant existing work, we had to look for research that has been done in the manufacturing area in general and the work involves applying blockchain technology. Our search was on the popular academic search engines such as Google Scholar, arXiv, and Research Gate. We searched for the following terms: ("Blockchain" OR "Distributed Ledger" OR "Smart Contract") AND ("Manufacturing" OR "Production" OR "M2M" OR "Factories" OR "Plants").  The result of our search included research papers published in journals and conferences. During the identification and selection process, we found several technologies are being used in the manufacturing industry and can be integrated with blockchain. Many researchers have already introduced blockchain-based applications to each one of these technologies. In the following subsections, we will describe what we found the most relevant to your discussed problem. An overview of all of these studies will be presented. For each one, we will describe the goal behind the work, the implementation approach, and the prototype if available.

\subsection{FabRec: A Prototype for Peer-to-Peer Network of Manufacturing Nodes \cite{Angrish2018a}}
\subsubsection{Motivation}
In FebRec, The goal is to build a trustless distributed network. Where different industrial organizations can collaborate and share information about manufacturing processes. Blockchain and smart contracts have been used to build the network. They stored information about machines, manufacturers and their capabilities. Through this network, all this information is shared transparently among participants. This will give a third party the ability to verify a certain capability of one manufacturer. The verification is done through a trial of past historic. This will help to make paperless contracts among participants using smart contracts. A participant of this network can be a human, manufacturing machine, a computing node or an agent representing any organization. The information about the machine's events stored as transactions. Three types of information exist machine asset information, machine utilization, and machine capability. Other types of information are stored inside the state variables of the smart contracts.
\subsubsection{Implementation}
They developed a prototype by building a small network using Ethereum as blockchain platform. The network consistent of 4 separate computers representing various fabrication service providers and two mining nodes. To simulate the machines, they used Arduino and a CNC machine controlled through MachineKit interface. The setup was intended to demonstrate how a smart contract can check for certain events relayed by the CNC machine. Then the contract triggers a command sent to the Arduino board. They also evaluate the performance of the prototype for two types of consensus algorithms: proof of work (POW) and proof of authority (POA). The evaluation used two metrics. The first one is the time it takes for a transaction to be included in a block on the blockchain. The second one is the time the block takes to reach a certain number of confirmations in the chain.
\subsubsection{Analysis}
This work focused on the horizontal integration of technology between many manufacturers. The prototype did not take into consideration a full automated manufacturing scenario. The authors did not discuss anything regarding the product is being manufactured.  However, they showed through the prototype the autonomous decision making and interaction of two physical devices on the blockchain network.

\newpage
\subsection{Toward a blockchain cloud manufacturing system as a peer to peer distributed network platform\cite{Li2018}}
\subsubsection{Motivation}
In this work, the authors used cloud manufacturing technology to be integrated with blockchain. They use it to build a distributed peer to peer network architecture. To improve the security and scalability of cloud platforms used by manufacturing service providers. This architecture provides a secure and distributed service sharing and trustable connection between end-users and service providers. Also, it provides the ability for self-trust, data integrity audit, data resilience, and secure data sharing. The architecture is made up of five layers namely; resource layer, perception layer, manufacturing layer, infrastructure layer, and application layer. They used smart contracts to write the rules of the agreement between the end-users and the service providers. These rules can contain the due date, quality measurement, and payment information.
\subsubsection{Implementation}
To demonstrate the implementation of proposed architecture. They showed a case study which includes five manufacturing service providers and 15 end users. Each service providers can provide three types of service namely; machining as a service, the technical issue as a service and welding as a service. The end users can send one request to the system at a time. The scenario begins when a customer wants to produce an industrial piece that can be manufactured with a CNC milling machine. He published information about the piece using the blockchain smart contract. Then, service providers send their offers to the customer (product cost and due date). When the customer accepted an offer from the service provider, it is executed as an atomic exchange. To simulate the physical machines they used CNC simulator \footnote{\url{https://cncsimulator.info/}}. For the blockchain platform, they also used MultiChain. In this work, a security and performance evaluation was carried to verify the proposed architecture. They discussed three security requirements, namely: confidentiality, integrity, and availability. This performance evaluation is done based on wallet creation and data encapsulation operation on the blockchain. 
\subsubsection{Analysis}
The focus of this work was to build a trusted peer to peer network to enable manufacturing as a service. The aim was to enhance communication between manufacturing parties. To overcome the issues resulted from the centralisation. The main benefit of using the blockchain in this work to enable secure data exchange. However, this work didn't take into consideration how architecture can be used to automate the production process itself.

\newpage
\subsection{Blockchain technology in the chemical industry: Machine-to-machine electricity market \cite{Sikorski2017}}
\subsubsection{Motivation}
One of the most highly cited papers with more than 250 citations. It is one of the first research works which used the M2M concept with blockchain. In this paper, the authors explored the applications of blockchain in relation to Industry 4.0. They build a proof of concept where a blockchain is used to facilitate the interaction between machines. The goal was to enable M2M electricity market. Where industrial plants are autonomously trading electricity with each other over a blockchain. The agreement between the producer and the consumer is done using smart contracts. Information about the energy consumption (in kWh) published by the machines stored as transactions in the blockchain. Each transaction as a fee (in USD) according to the agreement specified by the smart contract. 
\subsubsection{Implementation}
In their prototype, the scenario presented includes two electricity producers and one electricity consumer trading with each other over a blockchain. The physical machines were replaced with simulations of industrial processes in Aspen Plus (AP) \footnote{\url{https://www.aspentech.com/en/products/engineering/aspen-plus}}. They used MultiChain \footnote{\url{https://www.multichain.com/}} to build the private blockchain. The authors did not evaluate their prototype. 
\subsubsection{Analysis}
The focus of this work was on energy trading using M2M. The work doesn't provide any sort of framework or architecture that can be used on a large scale in manufacturing. This work was only to demonstrate that the blockchain can be used to facilitate the interaction between machines.
\bigbreak

@@

\newpage
\subsection{Industry 4.0: Smart Contract-based Industrial Internet of Things Process Management \cite{Garrocho2019}}
\subsubsection{Motivation}
In this study, the authors focused on the industrial machine to machine communication and how it can be improved by blockchain technologies. They introduced smart contract-based middleware for M2M communications to make it secure and decentralised. Through this middleware, IoT devices can communicate without the need or a trusted intermediary. Industrial Smart Contract Monitor (ISCOM) is the name of the middleware. It controls and executes contracts to order tasks from field devices. ISCOM monitors the field device states and executes actions based on a change in their state. It may also request a field device to perform service under a smart contract. All information about the actions and processes are recorded in the blockchain through smart contracts.

\subsubsection{Implementation}
 The authors present a proof of concept to simulate smart contracts in the industrial context. They used two Raspberry Pi 3 boards representing field devices. MQTT server for the communication between devices. For the blockchain network and smart contract implementation, the Ropsten Ethereum test network was used. The proof of concept worked in such a way that after the device changes its state, it publishes this change to the MQTT server. The middleware subscribes to the device publications and reviews the state according to the deployed smart contracts. Once the conditions of a smart contract satisfied, The middleware publishes messages to request a service from another field device. The other device picks this message published by the middleware and executes the operation accordingly. Two experiments were performed to evaluate the impact of latency and blocking time. The blocking time is the response time of the sensor device requests a change in the state of the smart contract.  The latency time is the delay time leading to communication between field devices and ISCOM. The experiments showed a high and variable blocking time for smart contracts. Which makes them unsuitable for M2M real-time communications.

\subsubsection{Analysis}
Unlike the other works, the focus here was on vertical communication within one factory. This work emphasises on the real-time requirement for M2M communications in industrial processes. The result showed that the smart contracts technology is still not mature enough to provide such essential requirement. Similar to the other works, the proof of concept was small a limited to only two devices.

\subsection{Summery}

\newpage
\section{Proposed Solution}
To answer the research questions, we will try to build a blockchain-based system in the area of manufacturing. The system collects, stores and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. For products, it provides the ability to track and trace each product throughout a production pipeline. Tracking the machines includes the status of the machines at any point in time. The system enables also the autonomous machine to machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using smart contract technologies and blockchain. It will be decentralized and distributed. The system will be serving the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

@@

\noindent Each machine and product has a digital profile. The profile of the product containing all related information about how the product has been manufactured. The profile will contains the full log of all the industrial tasks performed to a product. This include the machines information performed the tasks and the timestamps. Each product will have information tag attached to it to server as digital identity. This can be a bardcode or RFID. This tag will serve as identifier which links the physical product to its virtual twin on the network. Also machines will have a digital profile. The profile of the machine will contains related information about the industrial tasks performed by this machine. All the data in the network is stored on a blockchain and is available to anyone running the system software with a correct authentication.

@@

\newpage
\section{Implementation}
The figure \ref{fig:system_overview} shows a high level overview of the system compounds. The system consists of two main parts. The blockchain part, which is a private permissioned blockchain with a set of deployed smart contracts. The factory part, it is the infrastructure of the factory with all the machines and sensors. These two parts are communicating using Message Queuing Telemetry Transport (MQTT) protocol through the MQTT broker. MQTT is an open message protocol that enables the transmission of data in the form of messages between devices. The following sub-sections will explain each compound in details.

@@

\subsection{Factory Infrastructure}
This include different types the manufacturing resource like machines and sensors. We assume that all the resources are able to communicate using MQTT protocol. Each resource an send and receive messages with a certain topic. The messages send by these resources will be forwarded through the MQTT broker to a web application. Then it will send the corresponding transactions to the blockchain.

@@

\noindent To simulate such infrastructure in our implementation we are using Fischertechnik \footnote{https://www.fischertechnik.de/} factory model. It is a simulation of a factory used for learning and understanding industry 4.0 applications. It depicts the ordering process, the production process and the delivery process in digitised and networked steps \cite{Industry}. It consists of several modules like storage and retrieval stations, vacuum suction grippers, a high-bay warehouse, a multi-processing station with kiln, a sorting line with color detection, an environmental sensor, and a pivoting camera. The modules are controlled by six controllers. All of them networked within the factory and communicate with each other via MQTT.

\subsection{MQTT Broker}
A MQTT broker which received the messages from the factory and forward it into the web application. In the actual implementation we will use the broker provided by the Node-RED server \footnote{https://nodered.org/} but any other broker can be used.

\subsection{Front-End Web Application}
This is just a front end application used to communicate with the blockchain. It can be hosted hosted locally or in the cloud. The application is using standard front end technologies to build the user interfaces. To interact with the blockchain, it will use the Web3.js library \footnote{https://github.com/ethereum/web3.js/}. It is an Ethereum Javascript API implements the JSON-RPC protocol to connect and interact with any Ethereum blockchain networks. This application servers two proposes. The first one is to act like broker between the blockchain and the MQTT broker as the former can't connect directly to the blockchain. The second is to allow the actors to interact with the system and access the information.

\subsection{Truffle Framework}
We are using Truffle \footnote{https://github.com/trufflesuite/truffle} as development framework. Truffle is a development environment, testing framework and asset pipeline for Ethereum. It allow easy compiling, deployment and testing of smart contracts written in Solidity. Truffle build on the top of web3.js and provide more functionalities. This framework will be used to deploy the smart contracts into the blockchain. Also, it will be used to deploy the web3.js code of the web application.

@@

\section{Evaluation}
The qualitative evaluation of the proposed solution will by showing that the system is actually working. This includes details about implementation and how they comply with the proposed specifications and the requirements. Then the quantitative evaluation will be presented by analyzing the performance of the system and its scalability. Another important quantitative measure in the blockchain-based system is the cost measured by gas consumption. The pricing of gas has been removed from Quorum blockchain because it is a permissioned blockchain. However, the concept of the gas itself remains and can be measured.

@@

\newpage
\noindent  In \cite{Bai2019}, the authors presented an architecture for a light-weighted Blockchain-based platform for Industrial IoT (BPIIoT). The work address the security, trust, and island connection problems in the IIoT ecosystem. IT consists of two parts on-chain network and off-chain network to reduce network load and latency. The on-chain part provides communication services, and the data transmission between the nodes through the blockchain. Whereas, the off-chain provides data storage and complex processing which can't be done in the on-chain part. In this platform, any machine/equipment can add operation data to the blockchain, send transactions to the related smart contracts, and receive transactions from other nodes in the blockchain. Two applications discussed in details to demonstrate the proposed architecture.
\bigbreak

\noindent 
The first application is smart predictive maintenance. Where BPIIoT used to manage the equipment information and the maintenance process. They showed a use case about packaging platform based on the proposed BPIIoT architecture. It has two sensors connected with two robots to collect state data, such as temperature and vibration. This state information is being recorded in the on-chain network. The smart contract which serve as agreement between the equipment owner and the maintenance service provider, is monitoring the state information. When the temperature or vibration frequency exceeds a given threshold a certain number of times, a certain command is triggered. In this way, the equipment can request for maintenance services, replenishment or replacement of spare parts issued by the service provider/supplier.

>>>>

\section{Related Work}
The topic of this thesis involves two domains, the manufacturing industry, and the blockchain technology. To identify the relevant existing work, we had to look for research that has been done in the manufacturing area in general and the work involves applying blockchain technology. Our search was on the popular academic search engines such as Google Scholar, arXiv, and Research Gate. We searched for the following terms: ("Blockchain" OR "Distributed Ledger" OR "Smart Contract") AND ("Manufacturing" OR "Production" OR "M2M" OR "Factories" OR "Plants").  The result of our search included research papers published in journals and conferences. During the identification and selection process, we found several technologies are being used in the manufacturing industry and can be integrated with blockchain. Many researchers have already introduced blockchain-based applications to each one of these technologies. The main technologies are cloud manufacturing and machine-to-machine communication.  
\bigbreak

\noindent
In the following subsections, we will describe what we found the most relevant to the discussed problem. For each one of the studies, we are describing the goal behind the work, the implementation approach, and the prototype if available.

\subsection{FabRec: A Prototype for Peer-to-Peer Network of Manufacturing Nodes \cite{Angrish2018a}}

In this work, the goal is to build a trustless distributed network. Where different industrial organizations can collaborate and share information about manufacturing processes. The network was built using blockchain and smart contracts technologies. They stored information about machines, manufacturers and their capabilities. Through this network, all the information is shared transparently among participants. This will give a third party the ability to verify a certain capability of one manufacturer. The verification is done through a trial of past historic. This will help to make paperless contracts among participants using smart contracts. A participant of this network can be a human, manufacturing machine, a computing node, or an agent representing any organization. The information about the machine's events stored as transactions. Three types of information exist machine asset information, machine utilization, and machine capabilities. Other types of information like manufacturing related data is stored inside the state variables of the smart contracts.  They designed three 3 smart contract representations to represent the relationships between various participants of the network.
\bigbreak

\noindent
The prototype of this work was a small network built using Ethereum. To how machines on a decentralized network can autonomously interact without human involvement. The network consistent of 4 separate computers representing various fabrication service providers and two mining nodes. To simulate the machines, they used Arduino and a CNC machine controlled through MachineKit\footnote{https://www.machinekit.io/} interface. The setup was intended to demonstrate how a smart contract can check for certain events received by the CNC machine. Then the contract triggers a command sent to the Arduino board. The work also evaluates the performance of the prototype for two types of consensus algorithms: proof of work (POW) and proof of authority (POA). The evaluation used two metrics. The first one is the time it takes for a transaction to be included in a block on the blockchain. The second one is the time the block takes to reach a certain number of confirmations in the chain.
\bigbreak

\noindent
We think this work focused more on the horizontal integration of technology among many manufacturers.  The network does not contain data about the manufacturing process. Such data is being accessed through oracles from other existing Enterprise Resource Planning (ERP) systems and Manufacturing Execution Systems (MES). The work assumed that these existing IT systems are trustworthy. Regarding the prototype, it did not take into consideration a full automated manufacturing scenario. However, they showed through the prototype the autonomous decision making and interaction of two physical devices on the blockchain network.

\subsection{Toward a blockchain cloud manufacturing system as a peer to peer distributed network platform\cite{Li2018}}

The authors of this work integrated cloud manufacturing technology blockchain. The goal was to build a distributed peer to peer network architecture. To improve the security and scalability of cloud platforms used by manufacturing service providers. They proposed an architecture that provides a secure and distributed service sharing and trustable connection between end-users and service providers. Also, it provides the ability for self-trust, data integrity audit, data resilience, and secure data sharing. The architecture is made up of five layers namely; resource layer, perception layer, manufacturing layer, infrastructure layer, and application layer. They used smart contracts to write the rules of the agreement between the end-users and the service providers. These rules can contain the due date, quality measurement, and payment information.
\bigbreak

\noindent
To demonstrate the implementation of proposed architecture. The authors showed a case study which includes five manufacturing service providers and 15 end users. Each service providers can provide three types of service namely; machining as a service, the technical issue as a service and welding as a service. The end users can send one request to the system at a time. The scenario begins when a customer wants to produce an industrial piece that can be manufactured with a CNC milling machine. He published information about the piece using the blockchain smart contract. Then, service providers send their offers to the customer (product cost and due date). When the customer accepted an offer from the service provider, it is executed as an atomic exchange. To simulate the physical machines they used CNC simulator \footnote{\url{https://cncsimulator.info/}}. They used MultiChain as blockchain platform. In addition, a security and performance evaluation was carried to verify the proposed architecture. They discussed three security requirements, namely: confidentiality, integrity, and availability. The performance evaluation is done based on wallet creation time and data encapsulation operation on the blockchain. \bigbreak

\noindent
We think the focus of this work was on building a trusted peer to peer network to enable manufacturing as a service. The aim was to enhance communication between manufacturing parties. To overcome the issues resulted from the centralization. The main benefit of using the blockchain in this work to enable secure data exchange. However, this work didn't take into consideration how architecture can be used to automate the production process itself. \bigbreak

\noindent
A similar approach was presented in \cite{Barenji2019}. The goal also was to improve communication between manufacturing services users and manufacturing services providers. The proposed platform is explained in detail based on its architecture, consensus mechanism, and communication protocol. The use case of this work was in 3D printing manufacturing. They tested based on network performance and three practical scenarios. The results show that blockchain technologies can help to solve some existing problems found in the literature of cloud manufacturing.

\subsection{BPIIoT: A Light-Weighted Blockchain-Based
Platform for Industrial IoT \cite{Bai2019}}
The work addresses the security, trust, and island connection problems in the Industrial IoT (IIoT) ecosystem. The proposed architecture consists of two parts on-chain network and off-chain network to reduce network load and latency. The on-chain part provides data communication and transmission services. Whereas, the off-chain provides data storage and complex processing which can't be done in the on-chain part. In this platform, any machine/equipment can add operation data to the blockchain, send transactions to the related smart contracts, and receive transactions from other nodes in the blockchain. Two applications discussed in detail to demonstrate the proposed architecture.\bigbreak

\noindent 
One of the applications is smart predictive maintenance. Where the platform can be used to manage the equipment information and the maintenance process. The shown use case was about packaging platform based on the proposed BPIIoT architecture. It has two sensors connected with two robots to collect state data, such as temperature and vibration. This state information is being recorded in the on-chain network. The smart contract which serve as agreement between the equipment owner and the maintenance service provider, is monitoring the state information. When the temperature or vibration frequency exceeds a given threshold for a certain number of times, a command is triggered by the smart contract. In this way, the equipment can request for maintenance services, replenishment or replacement of spare parts issued by the service provider/supplier. The did not present the technical details about the implementation of this application. Overall this work did not focus on the internal manufacturing processes.

\subsection{Blockchain technology in the chemical industry: Machine-to-machine electricity market \cite{Sikorski2017}}

One of the most highly cited papers with more than 250 citations. It is one of the first research works which used the M2M concept with blockchain. In this paper, the authors explored the applications of blockchain in relation to Industry 4.0. They build a proof of concept where a blockchain is used to facilitate the interaction between machines. The goal was to enable M2M electricity market. Where industrial plants are autonomously trading electricity with each other over a blockchain. The agreement between the producer and the consumer is done using smart contracts. Information about the energy consumption (in kWh) published by the machines stored as transactions in the blockchain. Each transaction as a fee (in USD) according to the agreement specified by the smart contract. \bigbreak

\noindent In their prototype, the scenario presented includes two electricity producers and one electricity consumer trading with each other over a blockchain. The physical machines were replaced with simulations of industrial processes in Aspen Plus (AP) \footnote{\url{https://www.aspentech.com/en/products/engineering/aspen-plus}}. They used MultiChain \footnote{\url{https://www.multichain.com/}} to build the private blockchain. The authors did not evaluate their prototype. The focus of this work was on energy trading using M2M. The work doesn't provide any sort of framework or architecture that can be used on a large scale in manufacturing. This work was only to demonstrate that the blockchain can be used to facilitate the interaction between machines. \bigbreak

@@

\subsection{Industry 4.0: Smart Contract-based Industrial Internet of Things Process Management \cite{Garrocho2019}}

In this study, the authors focused on the industrial machine to machine communication and how it can be improved by blockchain technologies. They introduced smart contract-based middleware for M2M communications to make it secure and decentralised. Through this middleware, IoT devices can communicate without the need or a trusted intermediary. Industrial Smart Contract Monitor (ISCOM) is the name of the middleware. It controls and executes contracts to order tasks from field devices. ISCOM monitors the field device states and executes actions based on a change in their state. It may also request a field device to perform service under a smart contract. All information about the actions and processes are recorded in the blockchain through smart contracts.

@@

\noindent
 The authors present a proof of concept to simulate smart contracts in the industrial context. They used two Raspberry Pi 3 boards representing field devices. MQTT server for the communication between devices. For the blockchain network and smart contract implementation, the Ropsten Ethereum test network was used. The proof of concept worked in such a way that after the device changes its state, it publishes this change to the MQTT server. The middleware subscribes to the device publications and reviews the state according to the deployed smart contracts. Once the conditions of a smart contract satisfied, The middleware publishes messages to request a service from another field device. The other device picks this message published by the middleware and executes the operation accordingly. Two experiments were performed to evaluate the impact of latency and blocking time. The blocking time is the response time of the sensor device requests a change in the state of the smart contract.  The latency time is the delay time leading to communication between field devices and ISCOM. The experiments showed a high and variable blocking time for smart contracts. Which makes them unsuitable for M2M real-time communications.

\noindent
Unlike the other works, the focus here was on vertical communication within one factory. This work emphasises on the real-time requirement for M2M communications in industrial processes. The result showed that the smart contracts technology is still not mature enough to provide such essential requirement. Similar to the other works, the proof of concept was small and limited to only two devices.

\subsection{Summery}
It is evident from the works we discussed in this section that researchers have already presented some applications of blockchain in the manufacturing industry. The approaches as we saw vary wildly and each work looks at the problem from a different angle. Some of the works focused on the horizontal integration between manufacturing parties to enable the concept of manufacturing as a service. Either between manufacturers themselves or between manufacturers and customers. These works neglected the actual manufacturing process and focused more on the concept of trading. On the other hand, some works discussed the manufacturing process by enabling machine-to-machine communication over the blockchain. However, the use cases of these works were oversimplified and in most cases were limited in size (two machines). This does not reflect the actual communications between machines on a production line.

\section{Proposed Solution}
To answer the research questions, we will try to build a blockchain-based system in the area of manufacturing. The system collects, stores and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. For products, it provides the ability to track and trace each product throughout a production pipeline. Tracking the machines includes the status of the machines at any point in time. The system enables also the autonomous machine-to-machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using smart contract technologies and blockchain. It will be decentralized and distributed. The system will be serving the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

\noindent Each machine and product has a digital profile. The profile of the product contains all related information about how the product has been manufactured. The profile will contain the full log of all the industrial tasks performed to a product. This includes the machines information performed the tasks and the timestamps. Each product will have an information tag attached to it to serve as a digital identity. This can be a bardcode or RFID. This tag will serve as an identifier linking the physical product with its virtual twin on the network. Also the machines will have a digital profile. The profile of the machine will contain related information about the industrial tasks performed by this machine. All the data in the network is stored on a blockchain and is available to anyone running the system software with a correct authentication.

@@

\newpage
\section{Implementation}
The figure \ref{fig:system_overview} shows a high-level overview of the system compounds. The system consists of two main parts. The blockchain part, which is a private permissioned blockchain with a set of deployed smart contracts. The factory part is the infrastructure of the factory with all the machines and sensors. These two parts are communicating using Message Queuing Telemetry Transport (MQTT) protocol through the MQTT broker. MQTT is an open message protocol that enables the transmission of data in the form of messages between devices. The following sub-sections will explain each compound in details.

@@

\subsection{Factory Infrastructure}
This includes different types of the manufacturing resources like machines and sensors. We assume that all the resources are able to communicate using MQTT protocol. Each resource can send and receive messages with a certain topic. The messages sent by these resources will be forwarded through the MQTT broker to a web application. Then it will send the corresponding transactions to the blockchain.

@@

\noindent To simulate such infrastructure in our implementation we are using Fischertechnik \footnote{https://www.fischertechnik.de/} factory model. It is a simulation of a factory used for learning and understanding industry 4.0 applications. It depicts the ordering process, the production process and the delivery process in digitised and networked steps \cite{Industry}. It consists of several modules like storage and retrieval stations, vacuum suction grippers, high-bay warehouse, multi-processing station with kiln, sorting line with color detection, environmental sensor, and pivoting camera. The modules are managed by six controllers. All of them networked within the factory and communicate with each other via MQTT.

\subsection{MQTT Broker}
An MQTT broker receives the messages from the factory and forwards it into the web application. In the actual implementation we will use the broker provided by the Node-RED server \footnote{https://nodered.org/} but any other broker can be used.

\subsection{Front-End Web Application}
This is just a front end application used to communicate with the blockchain. It can be hosted locally or in the cloud. The application uses standard front end technologies to build the user interfaces. To interact with the blockchain, it will use the Web3.js library \footnote{https://github.com/ethereum/web3.js/}. It is an Ethereum Javascript API implements the JSON-RPC protocol to connect and interact with any Ethereum blockchain networks. This application servers two proposes. The first one is to act like broker between the blockchain and the MQTT broker as the former can not connect directly to the blockchain. The second is to allow the actors to interact with the system and access the information.

\subsection{Truffle Framework}
We are using Truffle \footnote{https://github.com/trufflesuite/truffle} as development framework. Truffle is a development environment, testing framework and asset pipeline for Ethereum. It allows easy compiling, deploying, and testing of smart contracts written in Solidity. Truffle is built on the top of web3.js and provides many functionalities. This framework will be used to deploy the smart contracts into the blockcain. Also, it will be used to deploy the web3.js code of the web application.

@@

\section{Evaluation}
The qualitative evaluation of the proposed solution will be achieved by showing that the system is actually working. This includes details about implementation and how they comply with the proposed specifications and the requirements. Then the quantitative evaluation will be presented by analyzing the performance of the system and its scalability. Another important quantitative measure in the blockchain-based system is the cost measured by gas consumption. The pricing of gas has been removed from Quorum blockchain because it is a permissioned blockchain. However, the concept of the gas itself remains and could be measured.

@@
